%-----------EXPERIENCE-----------
\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer II} {Nov 2021 -- Present}
      {Amazon (Prime Tech)} {Seattle, USA}
      \resumeItemListStart
        \resumeItem{Leading a 2-person team to improve customer engagement of a rewards program for Prime members with personalized recommendations.}
        % \resumeItem{Leading a team of 2 (including myself) to improve the customer engagement of a rewards program by showing personalized product recommendations to consented Prime customers.}
        \resumeItem{Led a 3-person team to design, develop, and launch a global multi-step reward program for Prime Day 2024, handling peak traffic of more than 10,000 TPS and driving over 240k orders and higher customer retention}
        % \resumeItem{Led a team of 3-person team to design, develop, and launch a new multi-step reward program for Prime Day 2024 in multiple marketplaces globally. The program received peak customer traffic of ~7000 TPS that contributed to more than 240k orders during Prime day.}
        \resumeItem{Improved response time of customer eligibility service from  5s (p99) to 50ms by implementing remote distributed cache with AWS ElastiCache (Redis) Cluster, resulting in 99\% reduction in customer-facing request timeouts.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Development Engineer II} {Dec 2018-- Nov 2021}
      {Amazon (Retail Pricing)} {Bangalore, India}
      \resumeItemListStart
        \resumeItem{Received \emph{SPS Day 1 Award} for my significant work on reducing time and cost of operations.}
        \resumeItem{Automated manual operations using Selenium Webdriver that helped operations team reduced a week (5 days) of manual effort to few (2-3) hours.}
        \resumeItem{Built automated experimentation tool that tested, evaluated and launched new configurations in minutes which previously took the whole day by operations team.}
        \resumeItem{Mentored and guided SDE-I to advance to the next level in their career.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Development Engineer I}{Sep 2017 -- Dec 2018}
      {Amazon (Retail Pricing)}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed a highly-responsive Electron-based desktop tool (replacing existing slow Firefox add-on) with feature improvements like pre-fetching, multi-instance, zero-click auto-updates, etc., that drastically increased operation team's productivity from spending 5 minutes on each work item to just few seconds.}
        \resumeItem{Enhanced performance and reduced latency of a work allocation tool that processed GBs of data daily, enabling efficient task assignment for an operations team of over 200 members.}
        \resumeItem{Mentored 2 SDE interns on their projects, leading to full-time job offers.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Development Engineer - Intern} {Feb 2017 -- Jul 2017}
      {Amazon (Retail Pricing)} {Bangalore, India}
      \resumeItemListStart
        \resumeItem{Re-designed and developed data warehouse solution to support report generation for write-heavy traffic, processing over 1TB/day of large-scale data. Reduced query time from 1 day to few minutes that helped internal operations team complete their analysis in days that previously took weeks/months. Optimized queries by partitioning the data at the day level using Amazon EMR (MapReduce with Apache Hive + Hadoop) loading data from S3 published by worker instances processing data streams from SQS.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd